---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# ggsegSchaefer

<!-- badges: start -->
[![R-CMD-check](https://github.com/ggsegverse/ggsegSchaefer/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/ggsegverse/ggsegSchaefer/actions/workflows/R-CMD-check.yaml)
[![r-universe](https://ggsegverse.r-universe.dev/badges/ggsegSchaefer)](https://ggsegverse.r-universe.dev/ggsegSchaefer)
<!-- badges: end -->

Schaefer Atlas for the ggsegverse Ecosystem.

## Installation

```{r, eval = FALSE}
# From r-universe
install.packages("ggsegSchaefer", repos = "https://ggsegverse.r-universe.dev")

# From GitHub
# install.packages("remotes")
remotes::install_github("ggsegverse/ggsegSchaefer")
```

## Atlases
Local-global parcellation of the human cerebral cortex (Schaefer et al., 2018) in 7-network and 17-network variants at 10 resolutions.

### Available variants

| Parcels | 7 Networks | 17 Networks |
|--------:|:-----------|:------------|
| 100 | `schaefer7_100()` | `schaefer17_100()` |
| 200 | `schaefer7_200()` | `schaefer17_200()` |
| 300 | `schaefer7_300()` | `schaefer17_300()` |
| 400 | `schaefer7_400()` | `schaefer17_400()` |
| 500 | `schaefer7_500()` | `schaefer17_500()` |
| 600 | `schaefer7_600()` | `schaefer17_600()` |
| 700 | `schaefer7_700()` | `schaefer17_700()` |
| 800 | `schaefer7_800()` | `schaefer17_800()` |
| 900 | `schaefer7_900()` | `schaefer17_900()` |
| 1000 | `schaefer7_1000()` | `schaefer17_1000()` |

### schaefer7_100

```{r schaefer7_100}
library(ggsegSchaefer)
plot(schaefer7_100())
```

### schaefer7_1000

```{r schaefer7_1000}
plot(schaefer7_1000())
```

### schaefer17_100

```{r schaefer17_100}
plot(schaefer17_100())
```

### schaefer17_1000

```{r schaefer17_1000}
plot(schaefer17_1000())
```
## Data source

Annotation files from [ThomasYeoLab/CBIG](https://github.com/ThomasYeoLab/CBIG) (fsaverage, resampled to fsaverage5).

- **Reference**: Schaefer et al. (2018) [doi:10.1093/cercor/bhx179](https://doi.org/10.1093/cercor/bhx179)
- **Date obtained**: 2020-03-27
